Concordance between observations and simulations in the evolution of the mass relation between supermassive black holes and their host galaxies

### 2022-07-25 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
final edit for post arxiv based on proof

\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consists of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. We first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the observations at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis supports the importance of both quasar and radio mode feedback prescriptions in the simulations. Finally, we highlight the importance of increasing the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases due to selection effects.
\end{abstract}
\keywords{Galaxy evolution (594); Active galaxies (17); Active galactic nuclei (16)}

\section{Introduction} \label{sec:intro}
The close correlations between the mass of supermassive black holes (\mbh) and the properties of their host galaxies (e.g., stellar mass, \smass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time. While, an {\it observed} evolution has been found since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in which the growth of BHs predates that of the host, other studies~\citep[e.g.,][]{Schramm2013, Sun2015, 2021ApJ...906..103L} predict that BHs grow commensurately with galaxies.
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009,  Ding2020,Li2021b}.

@@

In this study, we extend our previous work by adding recent measurements of hundreds of SDSS quasars at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program, and comparing the observational measurements with that from simulations. Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300 and Horizon-AGN. This paper is structured as follows. In Sections~\ref{sec:observations} and~\ref{sec:simulations}, we describe our observed and simulated samples. A direct comparison is performed and the result is presented in Section~\ref{sec:result}. The concluding remarks are presented in Section~\ref{sec:con}.

@@

A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS). HSC/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s. The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.  The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approach developed by D20 based on {\tt lenstronomy}. The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color. The results show that stellar templates of 1 and 0.625~Gyr can match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20). These best-fit models are used to estimate the stellar masses of the host galaxies. \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citet{Vestergaard2006}, in a consistent manner to that adopted for HSC sample. The mass ranges for the HST sample are log(\smass) $\in$ [9.5, 11.0] $M_{\odot}$, and log(\mbh) $\in$  [7.5, 9.0] $M_{\odot}$).
 We refer the reader to D20 for a more detailed description of the analysis.

@@

\begin{deluxetable*}{lccccc}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
}
\startdata
box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf mass resolution} \\
 dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
The `$\leq$' sign in the low accretion feedback mode of TNG means that the feedback efficiency follows a distribution with a maximum value of 0.2. Note that the radiative efficiencies are different in various simulations. Thus, different values are used for calculating the luminosity.
}
\end{deluxetable*}

\section{Simulations and comparison strategy}
\label{sec:simulations}
We introduce the simulation samples that are adopted in this study. All are based on larger-scale cosmological simulations, except the Semianalytic Model (SAM; see Section~\ref{subsec:SAM}). In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered. We note that each simulation adopts either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF. To make self-consistent comparisons, we ensure that the adopted IMF for both the simulations and the observations are consistent. The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparisons. For numerical simulation, the mass is the base material which is IMF independent.

@@

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at the intervals between which the BH mass grows by a fixed fraction. 
The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. Halos and galaxies are identified similar to that of MBII. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass. %, assuming a \cite{2003PASP..115..763C} IMF.

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} (IllustrisTNG, hereafter, TNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations. Note that TNG simulations employ a modified version of the Bondi formalism, with $c_s$ explicitly including a B term for these magneto-hydro simulations.

@@

The AGN feedback occurs in thermal, radio, and radiative modes. For high accretion rates, the feedback implementation is the same as Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs. However, at low accretion rates, the feedback implementation is substantially different from Illustris. Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic. In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W}. % at irregular intervals. 
The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$. Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG. Lastly, halo and galaxy identification, as well as calculation of galaxy stellar mass, is done in a similar manner to that of Illustris and MBII.

@@

We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.  Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours. Only galaxies with more than 50 particles are considered. With this approach for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture). This definition of stellar mass is commonly used in Horizon-AGN, whose stellar mass function is known~\citep{2017MNRAS.467.4739K} to be in good agreement with observations.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) for those at redshift $z=0.6$. A matched HSC sample is shown by the orange data points. The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space. Note that this is the first step of sample selection. We further use an AGN magnitude cut to assure that the simulation sample has a similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observations. We then use the same \smass\ cut to construct the final sample.
{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
}
\end{figure*}

@@

For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy which increases its mass. The binary interactions (fly-bys and mergers), among satellite sub-halos, are  also described by the model. In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}. The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr;  (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion). The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase. 
A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
$\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted.

{We assume BH seed $M_{seed}=100\,M_{\odot}$~\citep{Madau2001}  to be initially present in all galaxy progenitors at the initial redshift $z=15$. This constitutes an approximate way of rendering the effect of the collapse of PopIII stars. However, the detailed value of $M_{seed}$ has a negligible impact on the final BH masses as long as they remain in the range $M_{seed}=50-500\,M_{\odot}$.
}

The BH accretion is assumed to follow from the gas instabilities resulting from either galaxy interactions and disk instabilities, and is thus related to star formations channels 2-3: a fraction of the cold gas destabilized during galaxy encounters and through disc instabilities is in fact accreted onto the central BHs (with the remaining fraction fueling star formation through channels 2-3 described above). Such fractions and the corresponding timescales for accretion are computed as described in~\citet[][in Section 3]{Menci2014}.

The SAM adopted here implements a new and improved  model for the AGN feedback with respect to the previous versions~\citep{Menci2008}. In both versions, the basic assumption is that fast winds with velocity up to $10^{-1}c$ observed in the central regions of AGNs~\citep{Chartas2002, Pounds2003}  result in  supersonic outflows that compress the gas into a blast wave terminated by a leading shock front. This  moves outward with a lower but still supersonic speed, and sweeps out the surrounding medium. However, while in the earlier version of the SAM~\citep{Menci2016} the blast wave is assumed to expand into an isotropically distributed medium, in the new description of AGN feedback~\citep{Menci2019} the full two-dimensional structure of the gas disc and of the expanding blast wave is followed in detail. The main physical difference is that in the new model the large density of gas along the plane of the disc causes the blast wave expansion to stall in such a direction, while it expands with large velocities in the vertical direction. The resulting strong dependence of the total (integrated over directions) outflow rate on the AGN luminosity $L_{AGN}$ and on the gas content of the galaxy $M_{gas}$ is shown in Figure~\ref{fig:SAM}. Such a new AGN feedback model has been tested in detail against a state-of-the-art compilation of observed outflows in 19 galaxies with different measured gas and dynamical masses~\citep{Fiore2017}, allowing for a detailed, one-by-one comparison with the model predictions. This well tested AGN feedback model allowed us to derive, for each simulated galaxy in the SAM,  the outflow expansion and the mass outflow rates in different directions with respect to the plane of the disc.

\subsection{Application of observational measurement error and selection effects}\label{subsec:add_obs_eff}
To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples. We first inject random noise to the simulated catalog to mimic the scatter caused by measurement error. As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus their uncertainty levels are expected to be equivalent. We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.2~$dex, and $\Delta L_{\rm bol} = 0.03~$dex. Since the selection of the simulation sample based on $L_{\rm bol}$ has limited effects in this study (see the discussion in Section~\ref{sec:dis} and Figure~\ref{fig:offsets_nochange} for details), the AGN variability correction is not considered.

We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data. Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows:

>>>>

\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consists of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line active galactic nuclei (AGNs; $1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. We first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the observations at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model that considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis supports the importance of both quasar- and radio-mode feedback prescriptions in the simulations. Finally, we highlight the importance of increasing the sensitivity (e.g., using the James Webb Space Telescope), thereby pushing to lower masses and minimizing biases due to selection effects.
\end{abstract}
\keywords{Galaxy evolution (594); Active galaxies (17); Active galactic nuclei (16)}

\section{Introduction} \label{sec:intro}
The close correlations between the mass of supermassive black holes (BHs), \mbh, and the properties of their host galaxies (e.g., stellar mass, \smass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGNs) over a range of redshifts, with the intention to determine how and when the correlation emerges and evolves over cosmic time. While an {\it observed} evolution has been found since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in which the growth of BHs predates that of the host, other studies~\citep[e.g.,][]{Schramm2013, Sun2015, 2021ApJ...906..103L} predict that BHs grow commensurately with galaxies.
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009,  Ding2020,Li2021b}.

@@

In this study, we extend our previous work by adding recent measurements of hundreds of Sloan Digital Sky Survey (SDSS) quasars at $0.2<z<0.8$ based on wide and deep Hyper Suprime-Cam (HSC) imaging from the Strategic Subaru Program, and comparing the observational measurements with that from simulations. Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300, and Horizon-AGN. This paper is structured as follows. In Sections~\ref{sec:observations} and~\ref{sec:simulations}, we describe our observed and simulated samples. A direct comparison is performed and the result is presented in Section~\ref{sec:result}. The concluding remarks are presented in Section~\ref{sec:con}.

@@

A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS). The HST/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s. The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.  The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approach developed by D20 based on {\tt lenstronomy}. The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color. The results show that stellar templates of 1 and 0.625~Gyr can match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20). These best-fit models are used to estimate the stellar masses of the host galaxies. \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citet{Vestergaard2006}, in a consistent manner to that adopted for HSC sample. The mass ranges for the HST sample are log(\smass) $\in$ [9.5, 11.0] $M_{\odot}$, and log(\mbh) $\in$  [7.5, 9.0] $M_{\odot}$).
 We refer the reader to D20 for a more detailed description of the analysis.

@@

\begin{deluxetable*}{lccccc}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
}
\startdata
Box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
Particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf Mass Resolution} \\
 Dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 Baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN Feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
Maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
The `$\leq$' sign in the low accretion feedback mode of TNG means that the feedback efficiency follows a distribution with a maximum value of 0.2. Note that the radiative efficiencies are different in various simulations. Thus, different values are used for calculating the luminosity.
}
\end{deluxetable*}

\section{Simulations and comparison strategy}
\label{sec:simulations}
We introduce the simulation samples that are adopted in this study. All are based on larger-scale cosmological simulations, except the Semianalytic Model (SAM; see Section~\ref{subsec:SAM}). In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered. We note that each simulation adopts either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} initial mass function (IMF). To make self-consistent comparisons, we ensure that the adopted IMFs for both the simulations and the observations are consistent. The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparisons. For numerical simulation, the mass is the base material, which is IMF independent.

@@

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at the intervals between which the BH mass grows by a fixed fraction. 
The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. Halos and galaxies are identified similar to those of MBII. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass. %, assuming a \cite{2003PASP..115..763C} IMF.

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} (IllustrisTNG, hereafter, TNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous-generation simulations. Note that TNG simulations employ a modified version of the Bondi formalism, with $c_s$ explicitly including a B term for these magneto-hydro simulations.

@@

The AGN feedback occurs in thermal, radio, and radiative modes. For high accretion rates, the feedback implementation is the same as in Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs. However, at low accretion rates, the feedback implementation is substantially different from Illustris. Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic. In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W}. % at irregular intervals. 
The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$. Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG. Lastly, halo and galaxy identification, as well as calculation of galaxy stellar mass, is done in a similar manner to that of Illustris and MBII.

@@

We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.  Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbors. Only galaxies with more than 50 particles are considered. With this approach for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture). This definition of stellar mass is commonly used in Horizon-AGN, whose stellar mass function is known~\citep{2017MNRAS.467.4739K} to be in good agreement with observations.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) for those at redshift $z=0.6$. A matched HSC sample is shown by the orange data points. The light-green background cloud shows the {\it intrinsic} simulated number density in this parameter space. Note that this is the first step of sample selection. We further use an AGN magnitude cut to assure that the simulation sample has a similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observations. We then use the same \smass\ cut to construct the final sample.
{\it right}: similar to the left panel, but presenting the impact of selection on the HST sample.
}
\end{figure*}

@@

For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy which increases its mass. The binary interactions (fly-bys and mergers), among satellite sub-halos, are  also described by the model. In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}. The stars are converted from the gas through three channels: (1) quiescent star formation with long timescales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr;  (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion). The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation, which returns a fraction of the disk gas into a hot phase. 
A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
$\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted.

{We assume BH seed $M_{seed}=100\,M_{\odot}$~\citep{Madau2001}  to be initially present in all galaxy progenitors at the initial redshift $z=15$. This constitutes an approximate way of rendering the effect of the collapse of Population III stars. However, the detailed value of $M_{seed}$ has a negligible impact on the final BH masses as long as they remain in the range $M_{seed}=50-500\,M_{\odot}$.
}

The BH accretion is assumed to follow from the gas instabilities resulting from either galaxy interactions or disk instabilities, and is thus related to star formation channels 2-3: a fraction of the cold gas destabilized during galaxy encounters and through disk instabilities is in fact accreted onto the central BHs (with the remaining fraction fueling star formation channels 2-3 described above). Such fractions and the corresponding timescales for accretion are computed as described in~\citet[][their Section 3]{Menci2014}.

The SAM adopted here implements a new and improved  model for the AGN feedback with respect to the previous versions~\citep{Menci2008}. In both versions, the basic assumption is that fast winds with velocity up to $10^{-1}c$ observed in the central regions of AGNs~\citep{Chartas2002, Pounds2003}  result in  supersonic outflows that compress the gas into a blast wave terminated by a leading shock front. This  moves outward with a lower but still supersonic speed, and sweeps out the surrounding medium. However, while in the earlier version of the SAM~\citep{Menci2016} the blast wave is assumed to expand into an isotropically distributed medium, in the new description of AGN feedback~\citep{Menci2019} the full two-dimensional structure of the gas disk and of the expanding blast wave is followed in detail. The main physical difference is that in the new model the large density of gas along the plane of the disk causes the blast wave expansion to stall in such a direction, while it expands with large velocities in the vertical direction. The resulting strong dependence of the total (integrated over directions) outflow rate on the AGN luminosity $L_{AGN}$ and on the gas content of the galaxy $M_{gas}$ is shown in Figure~\ref{fig:SAM}. Such a new AGN feedback model has been tested in detail against a state-of-the-art compilation of observed outflows in 19 galaxies with different measured gas and dynamical masses~\citep{Fiore2017}, allowing for a detailed, one-by-one comparison with the model predictions. This well tested AGN feedback model allowed us to derive, for each simulated galaxy in the SAM,  the outflow expansion and the mass outflow rates in different directions with respect to the plane of the disc.

\subsection{Application of observational measurement error and selection effects}\label{subsec:add_obs_eff}
To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples. We first inject random noise to the simulated catalog to mimic the scatter caused by measurement error. As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus, their uncertainty levels are expected to be equivalent. We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.2~$dex, and $\Delta L_{\rm bol} = 0.03~$dex. Since the selection of the simulation sample based on $L_{\rm bol}$ has limited effects in this study (see the discussion in Section~\ref{sec:dis} and Figure~\ref{fig:offsets_nochange} for details), the AGN variability correction is not considered.

We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data. Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows.

Comparing with the HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample. We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it left}). (2) The $i$-band magnitudes of the AGN are bright (see Section~\ref{sec:hsc}). 
The specific selection is carried out as follows: a value of AGN $i$-band magnitude is chosen to make the sample selection such that the $L_{\rm bol}$ distribution is similar to the observations (see Section~\ref{sec:dis} for details).
Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
 (3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement. Finally, the HSC sample is split into three redshift bins for making comparisons, which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.

Comparing with the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window, which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example). Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., log(\mbh) between [7.7, 8.6] $M_{\odot}$). The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
